Designing Turk Experiments for Visual Statistical Inference

### 2013-06-21 paper_turk.tex
selection bias

\subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}. It is designed such a way that data from many different experiments can be stored in the same database. In total five separate tables are used. Table turk\_worker contains static information about each turk worker. The location information of each turk worker is stored in ip\_detals table. The information in this table is collected later based on the ip address of each turk worker. Table picture\_delais contains the static information about each lineup. Table feedback is a dynamic table that grows with the number of feedbacks from each turk worker. The multiple activities of the worker are recorded in turk\_activity table. This table also contains the codes provided to the workers once they finish the experiment. For the implementation of the web application we used MySQL database located on a local server.

@@

@@

\begin{table}[hbtp]
\caption{Information Collected from Each Individual}
\centering 
\begin{tabular}{lp{8cm}} 
\hline
Information &  Description \\ %[0.5ex] % inserts table %heading 
\hline
Identification & Nick name or any ID to determine the responses of an Individual \\
Response number & The number of the plot on the lineup plot which the individual thinks the most different than other 19 plots.\\ 
Reason of of choice & Reason why the individual chooses the plot \\
Confidence level & Confidence level of individual choice \\ 
Age group& The age group where the individual belongs \\
Education & The highest level of education completed \\
Gender & Male or female \\
Geographic Location & This information is collected through the ip address of the individual computer \\ 
Time taken & Time taken for each response\\
\hline
\end{tabular}
\label{tbl:data_info}
\end{table}

@@

Some cautious attempts are taken to add security to the data. Server side scripting language PHP is used to connect to database and access or save data. For transferring data from one form to another PHP session variables are used. Cookies are avoided carefully so that no important informations are saved in the cookies.

To prevent missing information and invalid input JavaScripts are used. For controlling some flow of the work such as showing various messages, JavaScripts are used as well. Careful consideration are made so that no important informations are stored in the java variable or function that could easily be revealed.

@@

\item Pay bonus

\item Appreciate work

\item Reply query email promptly

\item Block workers if necessary

@@

While selection bias is very important for some experimental study it is not much of an issue for experiment with lineups. If we examine the diversity of the participants in \ref{majumder:turk} we see that the turk data provide data from a very diverse population. Moreover it is observed in XXX that diversity is not much important for lineups as the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.

 may recruit from a specific geographical location

Setting up qualification may allow certain workers to do the task

Payment amount may affect the duration of the experiment which may avoid diversity in the geographical locations.

>>>>

\subsection{Database design} The design of the database to store the collected data is shown in Figure \ref{fig:turk_database_design}. It is designed such a way that data from many different experiments can be stored in the same database. In total five separate tables are used. Table turk\_worker contains static information about each turk worker. The location information of each turk worker is stored in ip\_detals table. The information in this table is collected later based on the ip address of each turk worker. Table picture\_delais contains the static information about each lineup. Table feedback is a dynamic table that grows with the number of feedbacks from each turk worker. The multiple activities of the worker are recorded in turk\_activity table. This table also contains the codes provided to the workers once they finish the experiment.

@@

The primary key in feedback table is produced by nick\_name and pic\_id since no workers are allowed to provide multiple feedbacks on the same lineup. In all other tables the first field names shown in Figure~\ref{fig:turk_database_design} are the primary keys. For the implementation of the web application we used MySQL database located on a local server.

@@

\begin{table}[hbtp]
\caption{Default information the web application collects from each individual}
\centering 
\begin{tabular}{lp{8cm}} 
\hline
Information &  Description \\ %[0.5ex] % inserts table %heading 
\hline
Identification & Nick name or any ID to determine the responses of an Individual \\
Response number & The number of the plot on the lineup plot which the individual thinks the most different than other 19 plots.\\ 
Reason of of choice & Reason why the individual chooses the plot \\
Confidence level & Confidence level of individual choice \\ 
Age group& The age group where the individual belongs \\
Education & The highest level of education completed \\
Gender & Male or female \\
Geographic Location & This information is collected through the ip address of the individual computer \\ 
Time taken & Time taken for each response\\
\hline
\end{tabular}
\label{tbl:data_info}
\end{table}

@@

Since the experiment is based on online participations and related to monetary affairs, it is important to maintain certain security for the data collection. The attempt to provide random data or irrelevant information as well as harmful actions need to be prevented.  Some cautious attempts are taken to add security to the data. Server side scripting language PHP is used to connect to database and access or save data. For transferring data from one form to another PHP session variables are used. Cookies are avoided carefully so that no important informations are saved in the cookies.

To prevent missing information and invalid input JavaScripts are used. Most of the cases options or combo boxes are used instead of free text boxes to avoid invalid input. This also made the task easy to perform and convenient for the workers. For controlling some flow of the work such as showing various messages, JavaScripts are used as well. Careful consideration are made so that no important informations are stored in the java variable or function that could easily be revealed.

@@

\item Not all the workers put the same effort while doing the task. Some workers spend much time and perform the task sincerely and follow the instructions very carefully. That effort is observable in their responses and time taken for each evaluations as well as from the textual feedbacks such as writing choice reasons in details. We recommend paying bonus to those workers in addition to the regular payment.

\item If a work is not worth paying bonus payment we still recommend to appreciate each work. Even when the task gets rejected a proper explanation of rejection along with an appreciation for at least trying to participate the experiment is very useful for a recruiter's good image.

\item Some workers may email to learn more about the experiment. Some times they may face technical troubles which needs to be taken care of promptly. A timely communication with worker is necessary and emails should be responded as  promptly as possible. It is important as they can report any trouble to IRB which may create unpleasant issues with the human subject experiment.

\item It is recommended to reject the task if it is not submitted as requirement. Some times this may produce dispute and the workers may become angry and demand payment. We recommend to be strict to the decision and for any further administrative control there is an option to block the worker if necessary. After all this is a work place and it is expected that the worker maintain the work place environment.

@@

While selection bias may influence the results of some experimental study it is not much of an issue for experiment with lineups. In terms of demographic factors and geographic location MTurk provides much diversity in the participants as we see in \cite{majumder:socio}. Moreover it is observed that the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.

% may recruit from a specific geographical location

%Setting up qualification may allow certain workers to do the task

%Payment amount may affect the duration of the experiment which may avoid diversity in the geographical locations.
